---
title: "Problem Set #9"
author: "Clayton Becker"
date: ""
urlcolor: blue
output: 
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", highlight = TRUE, warning = FALSE, message = FALSE, eval= FALSE)
```

\textcolor{red}{\textbf{Grade: /28}}

# Overview:

The purpose of this problem set is for you to understand how the backslash escape character (`\`) works in R strings, as well as to practice writing regular expressions. You will be using the `str_view_all()` function to see all the matches from your regex. You'll get practice combining character classes, quantifiers, anchors, ranges, groups, and more to build your regular expressions for each question.

In this problem set, you will be working on a shared repository with your homework group. We encourage you all to communicate with your group by creating issues on your shared repository. As usual, the requirements for this problem set are:

- You must create a separate branch (e.g., `dev_ozan_jaquette`, `dev_oj`) to do your work on
- Your `dev` branch must be pushed to the remote so we can see it
- You will turn in your files on the `main` branch (see final section), meaning you will need to merge in your work from `dev`


## Part I: Setting up repository

\textcolor{red}{\textbf{/1}}

1. Have one member of your group create a new private GitHub repository [here](https://github.com/organizations/anyone-can-cook/repositories/new) called `ps9_team_name` (fill in your team name). Make sure to initialize the repo with a `README.md` as well as a `.gitignore` file with the R template.

    The member who created the private repository should also give the other group members access to the repository by going on Settings > Manage Access > Invite teams or people. Then, all members of your group should clone this repository to your computers. Don't forget to change directories to where you want to save the repo before cloning it.

\textcolor{red}{\textbf{/1}}

2. Create a new **RStudio Project** for this repository. Add this `.Rmd` file to your project directory and rename it as `ps9_lastname_firstname.Rmd` (fill in your name). In your **RStudio Terminal**, create a new branch with your name or initials in the branch name (e.g., `dev_ozan_jaquette`, `dev_oj`) and use that branch to do all your work on. 

\textcolor{red}{\textbf{/1}}

3. Download the **Problem set R script template** available under the **Syllabus & Resources** section of the [class website](https://anyone-can-cook.github.io/rclass2/) (or click [here](https://anyone-can-cook.github.io/rclass2/assets/resources/ps_template.R)). Rename the downloaded `ps_template.R` to `ps9_lastname_firstname.R` (fill in your name) and save it inside your project directory.

    Open the R script and fill out your information in the header on top. Then, load the `tidyverse` library.


## Part II: Backslash (`\`) escape character

In this section, you will practice working with strings that include backslashes, such as for escaping characters or for writing special characters. You will be using both the `print()` and `writeLines()` functions to print out your string and compare the difference. This section is not specific to/does not involve regular expressions.

\textcolor{red}{\textbf{/1}}

1. Create a short string (could be a phrase or sentence) that contains both the single quote (`'`) and double quote (`"`) inside your string, and save it as an object called `string_with_quotes`. Use both `print()` and `writeLines()` to print out your string.  

    _Hint_: You will need to use a backslash to escape either the single quote (`'`) or the double quote (`"`) depending on if you used single or double quotes to enclose your string. 

\textcolor{red}{\textbf{/1}}

2. Create a short string (could be a phrase or sentence) that contains both the tab and newline special characters, and save it to `string_with_spchars`. Use both `print()` and `writeLines()` to print out your string.

\textcolor{red}{\textbf{/1}}

3. Create a string that contains your first name where each letter is separated by a backslash (e.g., `y\o\u\r\n\a\m\e`), and save it to `string_with_backslashes`. Use both `print()` and `writeLines()` to print out your string.

    _Hint_: Your `writeLines()` output should show single backslashes between each letter of your name.

\textcolor{red}{\textbf{/1}}

4. With respect to the previous questions, explain in general why the output created by the `print()` function differs from the output created by the `writeLines()` function.


## Part III: Matching characters

In this section and the next, you will practice writing regular expressions to match specific text. Use `str_view_all()` for all the following questions to show the matches.

\textcolor{red}{\textbf{/1}}

1. Show all matches to single quotes (`'`) in your `string_with_quotes` that you created in Part II.

\textcolor{red}{\textbf{/1}}

2. Show all matches to double quotes (`"`) in `string_with_quotes`.

\textcolor{red}{\textbf{/1}}

3. Show all matches to tab characters in `string_with_spchars`.

\textcolor{red}{\textbf{/1}}

4. Show all matches to newline characters in `string_with_spchars`.

\textcolor{red}{\textbf{/1}}

5. Show all matches to backslashes (`\`) in `string_with_backslashes`.


## Part IV: Regular expressions

\textcolor{red}{\textbf{/1}}

1. Copy the following code to create the character vector `text`:

    ```{r}
    text <- c("In 5... 4... 3... 2...",
              "It can cost anywhere between $50 to $100 (... or even $1k!)",
              "These are parenthesis (), while these are brackets []... I think.")
    ```

\textcolor{red}{\textbf{/1}}

2. Show all matches to a capital `I` at the beginning of the string.

\textcolor{red}{\textbf{/1}}

3. Show all matches to a period at the end of the string. 

\textcolor{red}{\textbf{/1}}

4. Show all matches to 1 or more digits.

\textcolor{red}{\textbf{/2}}

5. Show all matches to all dollar amounts, including the dollar sign and `k` if there is one (i.e., `$50`, `$100`, `$1k`)

\textcolor{red}{\textbf{/1}}

6. Show all matches to ellipses (`...`)

\textcolor{red}{\textbf{/2}}

7. Show all matches to parentheses, including the contents between the parentheses if there are any.

\textcolor{red}{\textbf{/2}}

8. Show all matches to words (define words as containing only letters, upper or lowercase)

\textcolor{red}{\textbf{/2}}

9. Show all matches to either a word that's 4 or more letters long _or_ ellipses.

\textcolor{red}{\textbf{/3}}

10. Show all matches to any digit or vowel (upper or lowercase) that repeats 2 times in a row (i.e., the same digit or vowel repeated twice in a row)


## Part V: Create a GitHub issue   


- Go to the [class repository](https://github.com/anyone-can-cook/rclass2_student_issues_w23/issues) and create a new issue.
- Please refer to [rclass2 student issues readme](https://github.com/anyone-can-cook/rclass2_student_issues_w23/blob/main/README.md) for instructions on how to post questions or things you've learned.
- You can either:
  - Ask a question that you have about this problem set or the course in general. Make sure to assign the instructors (@ozanj, @xochilthlopez, @joycehnguy, @augias) and mention your team (e.g., @anyone-can-cook/your_team_name).
  - Share something you learned from this problem set or the course. Please mention your team (e.g., @anyone-can-cook/your_team_name).
- You are also required to respond to at least one issue posted by another student.

- Paste the url to your issue here: https://github.com/anyone-can-cook/rclass2_student_issues_w23/issues/385
- Paste the url to the issue you responded to here: https://github.com/anyone-can-cook/rclass2_student_issues_w23/issues/383


# Knit to pdf and submit problem set  

**Knit to pdf** by clicking the "Knit" button near the top of your RStudio window (icon with blue yarn ball) or drop down and select "Knit to PDF"

You will need to submit both the `.Rmd` and `.pdf` files, as well as your `ps9_lastname_firstname.R` script. You should commit these items on your `dev` branch as you work through this problem set. In the end, merge your `dev` branch into `main` and then push to the remote `main` branch to submit. 
